%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Important note:
% This template requires the cv.cls file to be in the same directory as the
% .tex file. The cv.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{cv} % Use the custom cv.cls style
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=cyan,
    pdftitle={CV},
    pdfpagemode=FullScreen,
}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

%--------------------------------------------------------------------------------------
\name{James Stevenson}
\address{Columbus, OH, USA}
\address{james.sharpsteen@gmail.com}

\begin{document}

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Employment}
{\bf Bioinformatics Software Developer} \hfill {\em Sep. 2020 - present}\\
Institute for Genomic Medicine, Nationwide Children's Hospital
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
%--copy and paste this region  if you need more--
{\bf Georgia Institute of Technology} \hfill {\em expected May 2024}\\
Master of Science\\
Computer Science (specialization: Machine Learning)

{\bf University of Puget Sound} \hfill {\em May 2013}\\
Bachelor of Arts\\
Philosophy; Politics \& Government (emphasis: International Relations)
\end{rSection}

%--------------------------------------------------------------------------------
%    Publications
%-----------------------------------------------------------------------------------------------

\begin{rSection}{Publications}
{Matthew Cannon, \textbf{James Stevenson}, Kori Kuzma, Susanna Kiwala, Jeremy L Warner, Obi L Griffith, Malachi Griffith, Alex H Wagner. ``Normalization of Drug and Therapeutic Concepts with Thera-Py.'' JAMIA Open, vol. 6, no. 4 (2023).}\\
\\
{Matthew Cannon, \textbf{James Stevenson}, Kathryn Stahl, Rohit Basu, Adam Coffman, Susanna Kiwala, Joshua F McMichael, Kori Kuzma, Dorian Morrissey, Kelsy Cotto, Elaine R Mardis, Obi L Griffith, Malachi Griffith, Alex H Wagner. ``DGIdb 5.0: rebuilding the drug–gene interaction database for precision medicine and drug discovery platforms'' Nucleic Acids Research (2023).}
\end{rSection}

%--------------------------------------------------------------------------------
%    Conference Presentations
%-----------------------------------------------------------------------------------------------

\begin{rSection}{Conference Presentations}
{\bf Cancer Genomics Consortium Annual Meeting}{, St. Louis, MO} \hfill {\em August 2023}\\
{\em ``Overcoming challenges in semantic alignment of therapeutics knowledge using TheraPy''}\\
{Technologist Abstract Travel Award}\\
\\
{\bf CASCAID Regional Conference}{, Bellingham, WA} \hfill {\em August 2012}\\
{\em ``You Eat What You Are: Deconstruction, Dialectics, and Digestion''}\\
{Best Student Paper Award}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TEACHING SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Teaching}
{\bf Instructional Aide} \hfill {\em Jan. 2021 - Aug. 2021}\\
Georgia Institute of Technology\\
CS 6750: Human-Computer Interaction\\
\\
{\bf Instructor} \hfill {\em Sep. 2013 - May 2015}\\
University of Puget Sound\\
COMM 292: Intercollegiate Debate\\
\\
{\bf Debate Instructor} \hfill {\em July 2009 - July 2013}\\
Dixie State University\\
Sun Country Forensics Institute\\
\end{rSection}

\end{document}----------------------------

